\section{Problem Definition}
Suppose there are $N$ agents in an environment. 
The goal of this paper was to maximize the discounted cumulative reward the system obtained from the external environment.
This was calculated as:
\begin{equation}
G = \sum_{t=0}^T \gamma^t R_{t}^\mathrm{ex},
\end{equation}
where $R_{t}^\mathrm{ex}$ is a reward which $i$-th agent obtains at $t$, 
and $\gamma \in [0, 1]$ is the discount rate and $T$ is the terminal time.

Reward distribution is distributing $R_{t}^\mathrm{ex}$ to all the agents under the following constraints.
\begin{equation}
	\sum_{i=1}^N R_{it} = R_{t}^\mathrm{ex},
	\label{eq:reward_const}
\end{equation}
where $R_{it}$ is a reward which is distributed to $i$-th agent at time $t$.
For instance, in robot soccer, the environment give a reward 1 when an agent shoot a ball to the goal.
Each agent should receive the reward along to their contribution.

%Trusted third party is required to calculate $R_{it}$.
In most of MARL communication methods, the policy of reward distribution is determined by a centralized agent.
For example, QUICR \citep{agogino2006quicr} and COMA \citep{foerster2017counterfactual} distribute $R_{it}$ according to counterfactal reward, difference of reward between an agent made an action and not.
The value of counterfactual reward is calculated by centralized agent, called {\em trusted third party} (TTP).

In a peer-to-peer environment such as inter-industry and -countery trade, they cannot place a TTP. 
Hence, another framework required to actualize reward distirbution without TTP.

% FIXME ここではまだ external environment の話はしていない

% 金銭のように環境から与えられる報酬の量は限られており、これらをエージェント間で分配するという問題を解いているという話を加える
%Suppose there are $N$ agents interacting in an environment. 
%The goal of this paper was to maximize the discounted cumulative reward the system obtained from the external environment.
%This was calculated as:
%\begin{equation}
%G = \sum_{i=1}^N \left[ \sum_{t=0}^T \gamma^t R_{it}^\mathrm{ex} \right],
%\end{equation}
%where $R_{it}^\mathrm{ex}$ is an external reward which $i$-th agent obtains at $t$, and $\gamma \in [0, 1]$ is the discount rate and $T$ is the terminal time.
